Dynamic stiffness matrix based on the extended separation-of-variables solution for the free vibration of orthotropic rectangular thin plates

### 2025-06-30 Paper7.tex
Proof read at last - comments in latex; make sure tables fit.

\newcommand{\kph}{~\unit{\kilo\metre\per\hour}\xspace}
\newcommand{\um}{~\unit{\metre}\xspace}
\newcommand{\ukg}{~\unit{\kilogram}\xspace}
\newcommand{\urho}{~\unit{\kilogram\per\meter}\xspace}
\newcommand{\uI}{~\unit{\kilogram\square\metre}\xspace}
\newcommand{\urd}{~\unit{\newton\square\metre}\xspace}
\newcommand{\ustif}{~\unit{\newton\per\metre}\xspace}
\newcommand{\udamp}{~\unit{\newton\second\per\metre}\xspace}
\newcommand{\DAF}{\textnormal{DAF}}
% Hacky - is there a better upright i?
%\newcommand{\ii}{\textnormal{i}}
\newcommand{\id}{\mathrm{d}\mkern1mu}
\newcommand{\ii}{\mathrm{i}\mkern1mu}
\newcommand{\nukg}{\unit{\kilogram}\xspace}
\newcommand{\nustif}{\unit{\newton\per\metre}\xspace}
\newcommand{\nudamp}{\unit{\newton\second\per\metre}\xspace}
\newcommand{\nugpa}{\si{\giga\pascal}\xspace}
\begin{document}

% I made some comments about x/L being xi - it's not used much so you can ignore these.
% There are some cases where I added text in [square brackets] and not necessarily in a latex comment
% Check the bib file - two references had no journal - I added these as XXXX
% Section 4 does too much - could you consider splitting this section up a bit? 
% I did add some more subsubsections to try structure section 4 a bit better, but I'm not sure it's optimal yet.
\begin{frontmatter}
\title{The dynamic stiffness matrix based on the extended separation-of-variables type solution for the free vibration of orthotropic rectangular thin plates}
\author[1]{Shiyi Mei}\ead{shiyi.mei1@monash.edu}
\author[1]{Colin Caprani\corref{cor1}}\ead{colin.caprani@monash.edu}
\author[2]{Daniel Cantero}\ead{daniel.cantero@ntnu.no}
\cortext[cor1]{Corresponding author}
\affiliation[1]{organization={Department of Civil Engineering, Monash University},city={Melbourne},state={Victoria},country={Australia}}
\affiliation[2]{organization={Department of Structural Engineering, Norwegian University of Science \& Technology NTNU},city={Trondheim}, country={Norway}}
\begin{abstract}
The dynamic stiffness matrix (DSM) based on the extended separation-of-variables (SOV) type mode solution is developed for the free vibration analysis of an orthotropic rectangular thin plate with general homogeneous boundary conditions.  
The method combines the advantages of the DSM method and the SOV method.
The SOV type solution satisfies the governing differential equation derived from Rayleigh’s principle and is used to formulate the dynamic stiffness matrices.
Owing to the characteristics of the SOV type solution, the fully clamped boundary condition problem associated with the Wittrick–Williams algorithm is resolved. 
The enhanced algorithm is further proposed to solve dynamic stiffness matrices, rather than solving eigenvalue equations.
A numerical technique for mode shape computation is also introduced.
The accuracy of the proposed method is validated through numerical experiments.

@@

Besides the approximation methods, several analytical methods have been developed over the past decades, including the Kantorovich-Krylov method \cite{kantorovich1958approximate,kerr1968extension}, the symplectic eigenfunction expansion method \cite{zhong1995new,xing2009new2}, the separation-of-variable (SOV) method \cite{xing2009new}, the dynamic stiffness matrix (DSM) method \cite{banerjee1997dynamic}, and series expansion-based methods \cite{xing2022review}.
The series expansion-based methods include the superposition method \cite{timoshenko1940theory,gorman2005free}, Fourier series method \cite{khov2009accurate,li2009exact}, the finite integral transform method \cite{li2009finite,zhong2013free}, and other series methods. 
These methods represent the plate displacement in terms of an infinite series and mostly are capable of handling any general boundary conditions. 
However, sufficient truncation of the series is required to ensure the accuracy and convergence of the results, and the eigenvalue equation is generally difficult to express explicitly.
Therefore, solving the corresponding eigenvalue problem can be computationally expensive.

Despite being a powerful method for the dynamic analysis of plate assemblies, the finite element method (FEM) requires a sufficient number of elements and is computationally expensive to accurately capture higher-order modes.
Thus, the DSM method was developed as an accurate and efficient analytical approach to alternatively solve complex plate structures \cite{boscolo2011dynamic,fazzolari2013exact}. 
The DSM can be considered as an analytical FEM since the mode functions of the plate are expressed by analytical solutions, where Levy-type solution \cite{ghorbel2015dynamic} or components of infinite Fourier series \cite{banerjee2015dynamic,liu2016free} are applied.
To avoid solving the cumbersome transcendental frequency equation directly, the Wittrick-Williams (W-W) algorithm \cite{wittrick1971general} is applied to the eigenvalue problem.
The W-W algorithm determines the lower and upper bounds of natural frequencies rather than solving the frequency equation directly. 
Thus, the DSM has the potential to be effectively and systematically solved using the W-W algorithm.
However, a critical part in applying the W-W algorithm is to priorly determine all natural frequencies of the fully clamped structure within the interested frequency range.
Strategies such as using a sufficiently fine mesh or including a sufficient number of terms in series expansions \cite{banerjee2015dynamic} can ensure that all fully clamped frequencies are accounted for, thereby maintaining the accuracy of the algorithm. However, these approaches are computationally expensive and complex, posing a significant obstacle to the wider adoption and application of the DSM method based on the W-W algorithm \cite{han2018improved}.
To resolve the fully clamped plate problem, \citet{liu2015exact} suggested that the frequencies can be indirectly obtained from the simply supported plate problem, where the Navier solution serves as the analytical solution. This provides a significant enhancement to the W-W algorithm, increasing the efficiency of applying DSM methods. 
However, the solutions are not explicit and closed-form, but are expressed in an infinite series form, where a sufficient number of truncation terms is required to ensure accuracy.

@@

In this study, the SOV method is extended to analyze the vibrations of plates with elastically restrained edges.
The extended SOV type solution is then employed to construct the dynamic stiffness matrices, which accommodate all general homogeneous boundary conditions.
By taking advantage of both the SOV and DSM methods, an enhanced W-W algorithm is developed to solve the eigenvalue problem without directly solving the eigenvalue equations.
This enhanced approach resolves the challenge of determining fully clamped frequencies, a well-known limitation in the application of the  W-W algorithm.
In addition, a novel numerical technique has been proposed to compute the mode shape coefficients.

@@

Instead of solving the free vibration of the thin orthotropic plate using \Cref{eq:governing_EOM}, it is suggested that the vibration of the thin plate can also be solved using the Rayleigh quotient variational principle \cite{xing2018overall}:
%
\begin{equation}\label{eq:Rayleigh}
	\begin{split}
		\delta U_{mag} &= \omega^2\,\delta T_0,
	\end{split}
\end{equation}
%
where $\delta$ denotes variation, $U_{mag}$ is the magnitude of the potential energy of the plate, and $\omega^2 T_0$ represents the magnitude of the kinetic energy of the plate.
The potential energy of the plate can be expressed as \cite{xing2020extended}:
%
\begin{equation}\label{eq:poten_energy}
	\begin{split}
		U^{I} &= \frac{1}{2}\iint \Big[D_{11}\left(\frac{\partial^2 W}{\partial x^2}\right)^2 + 2D_{12}\frac{\partial^2 W}{\partial x^2}\frac{\partial^2 W}{\partial y^2} + D_{22}\left(\frac{\partial^2 W}{\partial y^2}\right)^2 \\
		&\qquad + 4D_{66}\left(\frac{\partial^2 W}{\partial x \partial y}\right)^2\Big] \, \mathrm{d}x \, \mathrm{d}y.
	\end{split}
\end{equation}
%
And the kinetic energy is:
%
\begin{equation}\label{eq:kine_energy}
	\begin{split}
		T &= \frac{1}{2}\iint \rho h \left(\frac{\partial W}{\partial t}\right)^2 \, \mathrm{d}x \, \mathrm{d}y.
	\end{split}
\end{equation}

Assuming the solution of the deflection $ W(x, y; t) = w(x, y) e^{i \omega t} $ for harmonic plate motion, 
where $ \ii = \sqrt{-1} $, $ w(x, y) $ is the mode shape, and $ \omega $ is the radial frequency.  
By substituting $ W(x, y; t) = w(x, y) e^{i \omega t} $ into \Cref{eq:poten_energy,eq:kine_energy} and expressing the system in dimensionless coordinates, we have:
%
\begin{equation}\label{eq:poten_energy_mag}
	\begin{split}
		U_{\text{mag}}^{I} &= \frac{ab}{2} \iint \left[ \frac{D_{11}}{a^4} \left( \frac{\partial^2 w}{\partial \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2} \frac{\partial^2 w}{\partial \xi^2} \frac{\partial^2 w}{\partial \eta^2} + \frac{D_{22}}{b^4} \left( \frac{\partial^2 w}{\partial \eta^2} \right)^2 \right. \\
		&\quad \left. + \frac{4 D_{66}}{a^2 b^2} \left( \frac{\partial^2 w}{\partial \xi \partial \eta} \right)^2 \right] \, \mathrm{d} \xi \, \mathrm{d} \eta,
	\end{split}
\end{equation}
%
and
%
\begin{equation}\label{eq:kine_energy_mag}
	\begin{split}
		T &= \omega^2 \frac{ab}{2} \rho h \iint w^2 \, \mathrm{d} \xi \, \mathrm{d} \eta = \omega^2 T_0
	\end{split},
\end{equation}
%
The separable form of the mode shape function $ w(\xi, \eta)$ is given by:
%
\begin{equation}\label{eq:displace_func}
	w(\xi, \eta) = \phi(\xi) \psi(\eta),
\end{equation}
%
where $ \phi(\xi) $ and $\psi(\eta) $ can be expressed as:
\begin{subequations}\label{eq:phi_psi_solution}
	\begin{align}
		\phi(\xi) &= A_1 \sin{(\alpha_1 \xi)} + A_2 \cos{(\alpha_1 \xi)} + A_3 \sinh{(\beta_1 \xi)} + A_4 \cosh{(\beta_1 \xi)},\label{eq:phi_solution1}\\
		\psi(\eta) &= B_1 \sin{(\alpha_2 \eta)} + B_2 \cos{(\alpha_2 \eta)} + B_3 \sinh{(\beta_2 \eta)} + B_4 \cosh{(\beta_2 \eta)}. \label{eq:phi_solution2}
	\end{align}
\end{subequations}

Based on \Cref{eq:Rayleigh}, the frequencies $\omega_x$ and $\omega_y$, corresponding to the mode shapes $\phi(\xi)$ and $\psi(\eta)$, respectively, are assumed to be independent of each other.

@@

The vertical translational and rotational springs at the $\xi = -1$ end are defined as $k^v_{\xi = -1}$ and $k^r_{\xi = -1}$, respectively, and at the $\xi = 1$ end as $k^v_{\xi = 1}$ and $k^r_{\xi = 1}$, respectively. 

@@

@@

@@

		&\qquad \left.  + \frac{4 D_{66}}{a^2 b^2} \left( \frac{\partial^2 w}{\partial \xi \partial \eta} \right)^2 \right] \, \id\xi \, \id\eta + ab \int \left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=1}}{a} \left( w \right)^2 \right]_{\xi=1} \, \id \eta \\

@@

		U_{mag}&=U^{I}_{mag}+U^{II}_{mag}\\
		&=\frac{ab}{2} \int_{-1}^{1} \left[ \frac{D_{11}}{a^4}I_1 \left( \frac{\id^2\phi }{\id \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2}I_2 \frac{\id^2\phi }{\id \xi^2}\phi  + \frac{D_{22}}{b^4}I_4  \phi^2 \right. \\
		&\qquad \left. + \frac{4 D_{66}}{a^2 b^2}I_3 \left( \frac{\id \phi }{\id \xi}\right)^2 \right] \, \id\xi +abI_1 \left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=-1}}{a} \left( \phi \right)^2\right]_{\xi=-1}\\
		&\qquad+abI_1 \left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=1}}{a} \left( \phi \right)^2\right]_{\xi=1},

@@

@@

@@

		\delta U_{mag} &= \omega_x^2 \, \delta T_0.

@@

By substituting \Cref{eq:poten_energy_tolx2,eq:kine_energyx} into \Cref{eq:Rayleighx}, and relieving $\delta \phi$ and $\delta\frac{\id  \phi}{\id \xi}$ in \Cref{eq:Rayleighx} by variation calculus, yields:

@@

@@

By substituting $\phi(\xi) = A e^{\mu \xi}$ into \Cref{eq:ODEx}, yields:

@@

The solution for $\mu$ can be expressed as:

@@

		&\qquad+ \frac{2k^v_{\xi=-1}}{a} I_1 \left(\phi\right)_{\xi=-1}

@@

		\left( \frac{D_{12}}{a^2b^2} I_2 \phi + \frac{D_{11}}{a^4} I_1 \frac{\partial^2 \phi}{\partial \xi^2} \right) 
		\Big|^{\xi=1}_{\xi=-1} 
		&+ \frac{2k^r_{\xi=-1}}{a^3} I_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=-1} \\
		& \qquad\frac{2k^r_{\xi=1}}{a^3} I_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=1} = 0.

@@

Substituting \Cref{eq:phi_solution1} into \Cref{eq:boundaryx}, and denoting $ k^{v*}_{\xi} = \frac{2a^3 k^v_{\xi}}{D_{11}} $, $ k^{r*}_{\xi} = \frac{2a k^r_{\xi}}{D_{11}} $, $ S_{\alpha_1}=\sin\alpha_1 $, $ C_{\alpha_1}=\cos\alpha_1 $, $ Sh_{\alpha_1}=\sinh\alpha_1 $, $ Ch_{\alpha_1}=\cosh\alpha_1 $, $S_{\beta_1}= \sin\beta_1 $, $C_{\beta_1}=\cos\beta_1$, $Sh_{\beta_1}=\sinh\beta_1 $, and $  Ch_{\beta_1}=\cosh\beta_1 $, we have:

@@

However, solving these transcendental equations are cunmbersome and tedious, thus the DSM is introducted to avoid the ineffective computation.

To develop its dynamic stiffness matrix, with the help of \Cref{eq:phi_solution1}, the vertical displacement and rotation corresponding to the mode shape $\phi(\xi)$ along the $x$-direction at edges $\xi = -1$ and $\xi = 1$ can be expressed as:
%
\begin{equation}\label{eq:UBx}
	\begin{split}
		\begin{Bmatrix}
			\phi_{\xi=-1}\\\frac{\id \phi}{\id \xi}_{\xi=-1}\\\phi_{\xi=1}\\\frac{\id \phi}{\id \xi}_{\xi=1}
		\end{Bmatrix}
		= \begin{bmatrix}
			-S_{\alpha_1}&C_{\alpha_1}&-Sh_{\beta_1}&Ch_{\beta_1}\\
			\alpha_1 C_{\alpha_1}/a&\alpha_1S_{\alpha_1}/a&\beta_1Ch_{\beta_1}/a&-\beta_1Sh_{\beta_1}/a\\
			S_{\alpha_1}&C_{\alpha_1}&Sh_{\beta_1}&Ch_{\beta_1}\\
			\alpha_1 C_{\alpha_1}/a&-\alpha_1S_{\alpha_1}/a&\beta_1Ch_{\beta_1}/a&\beta_1Sh_{\beta_1}/a
		\end{bmatrix}
		\begin{Bmatrix}
			A_1\\A_2\\A_3\\A_4
		\end{Bmatrix} ,
	\end{split}
\end{equation}
%
or,
%
\begin{equation}\label{eq:UBx1}
	\mathbf{\delta}_x= \mathbf{Q}_x\mathbf{A}.
\end{equation}
%
Note that the eigenvector $\mathbf{A}$ can be expressed by multiplying the inverse matrix $\mathbf{Q}_x^{-1}$ on the left side of \Cref{eq:UBx1}, and then substituting $\mathbf{A}$ into \Cref{eq:ABx1}, we obtain:
%
\begin{equation}\label{eq:DSM_eqx}
	\mathbf{R}_x \mathbf{A}=\mathbf{R}_x\mathbf{Q}_x^{-1}\mathbf{\delta}_x = \mathbf{0}.
\end{equation}
%
where the dynamic stiffness matrix, denoted as $\mathbf{K}_x = \mathbf{R}_x\mathbf{Q}_x^{-1}$, can be obtained from \Cref{eq:DSM_eqx}. 
This matrix can be used to compute the natural frequencies of the system instead of solving the eigenvalue equation, 
and the method for the computation will be given in \Cref{sec:WWA}.

\subsection{Dynamic stiffness matrix corresponding to $\omega_y$}\label{sec:DSMy}
In this section, the mode shape $\phi(\xi)$ derived in $\Cref{sec:DSMx}$ is utilized to obtain the dynamic stiffness matrix in the $y$-direction.  
The vertical translational and rotational springs at $\eta = -1$ are denoted as $k^v_{\eta = -1}$ and $k^r_{\eta = -1}$, respectively, while those at $\eta = 1$ are represented by $k^v_{\eta = 1}$ and $k^r_{\eta = 1}$.

>>>>

\newcommand{\kph}{~\unit{\kilo\metre\per\hour}\xspace}
\newcommand{\um}{~\unit{\metre}\xspace}
\newcommand{\ukg}{~\unit{\kilogram}\xspace}
\newcommand{\urho}{~\unit{\kilogram\per\meter}\xspace}
\newcommand{\uI}{~\unit{\kilogram\square\metre}\xspace}
\newcommand{\urd}{~\unit{\newton\square\metre}\xspace}
\newcommand{\ustif}{~\unit{\newton\per\metre}\xspace}
\newcommand{\udamp}{~\unit{\newton\second\per\metre}\xspace}
\newcommand{\DAF}{\textnormal{DAF}}
% Hacky - is there a better upright i?
%\newcommand{\ii}{\textnormal{i}}
\newcommand{\id}{\mathrm{d}\mkern1mu}
\newcommand{\ii}{\mathrm{i}\mkern1mu}
\newcommand{\nukg}{~\unit{\kilogram}\xspace}
\newcommand{\nustif}{~\unit{\newton\per\metre}\xspace}
\newcommand{\nudamp}{~\unit{\newton\second\per\metre}\xspace}
\newcommand{\nugpa}{~\si{\giga\pascal}\xspace}
\begin{document}

% I made some comments about x/L being xi - it's not used much so you can ignore these.
% There are some cases where I added text in [square brackets] and not necessarily in a latex comment
% Check the bib file - two references had no journal - I added these as XXXX
% Section 4 does too much - could you consider splitting this section up a bit? 
% I did add some more subsubsections to try structure section 4 a bit better, but I'm not sure it's optimal yet.
\begin{frontmatter}
\title{Dynamic stiffness matrix based on the extended separation-of-variables solution for the free vibration of orthotropic rectangular thin plates}
\author[1]{Shiyi Mei}\ead{shiyi.mei1@monash.edu}
\author[1]{Colin Caprani\corref{cor1}}\ead{colin.caprani@monash.edu}
\author[2]{Daniel Cantero}\ead{daniel.cantero@ntnu.no}
\cortext[cor1]{Corresponding author}
\affiliation[1]{organization={Department of Civil Engineering, Monash University},city={Melbourne},state={Victoria},country={Australia}}
\affiliation[2]{organization={Department of Structural Engineering, Norwegian University of Science \& Technology NTNU},city={Trondheim}, country={Norway}}
\begin{abstract}
The dynamic stiffness matrix (DSM) based on the extended separation-of-variables (SOV) type mode solution is developed for the free vibration analysis of an orthotropic rectangular thin plate with general homogeneous boundary conditions.  
The method combines the advantages of the DSM method and the SOV method.
The SOV type solution satisfies the governing differential equation derived from Rayleigh’s principle and is used to formulate dynamic stiffness matrices.
Owing to the characteristics of the SOV type solution, the fully clamped boundary condition problem associated with the Wittrick–Williams algorithm is resolved. 
The enhanced algorithm is further proposed to solve dynamic stiffness matrices, rather than solving eigenvalue equations.
A numerical technique for mode shape computation is also introduced.
The accuracy of the proposed method is validated through numerical experiments.

@@

Besides the approximation methods, several analytical methods have been developed over past decades, including the Kantorovich-Krylov method \cite{kantorovich1958approximate,kerr1968extension}, the symplectic eigenfunction expansion method \cite{zhong1995new,xing2009new2}, the separation-of-variable (SOV) method \cite{xing2009new}, the dynamic stiffness matrix (DSM) method \cite{banerjee1997dynamic}, and series expansion-based methods \cite{xing2022review}.
The series expansion-based methods include the superposition method \cite{timoshenko1940theory,gorman2005free}, Fourier series method \cite{khov2009accurate,li2009exact}, the finite integral transform method \cite{li2009finite,zhong2013free}, and other series methods. 
These methods represent the plate displacement in terms of an infinite series and mostly are capable of handling any general boundary conditions. 
However, sufficient truncation of the series is required to ensure the accuracy and convergence of the results, and the eigenvalue equation is generally difficult to express explicitly.
Therefore, solving the corresponding eigenvalue problem can be computationally expensive.

Despite being a powerful method for the dynamic analysis of plate assemblies, the finite element method (FEM) requires a sufficient number of elements and is computationally expensive to accurately capture higher-order modes.
Thus, the DSM method was developed as an accurate and efficient analytical approach to alternatively solve complex plate structures \cite{boscolo2011dynamic,fazzolari2013exact}. 
The DSM can be considered as an analytical FEM since the mode functions of the plate are expressed by analytical solutions, where Levy-type solution \cite{ghorbel2015dynamic} or components of infinite Fourier series \cite{banerjee2015dynamic,liu2016free} are applied.
To avoid solving the cumbersome transcendental frequency equation directly, the Wittrick-Williams (W-W) algorithm \cite{wittrick1971general} is applied to the eigenvalue problem.
The W-W algorithm determines the lower and upper bounds of natural frequencies to arbitrary precision rather than solving the frequency equation directly. 
Thus, the DSM has the potential to be effectively and systematically solved using the W-W algorithm.
However, a critical part in applying the W-W algorithm is to determine all natural frequencies of the fully clamped structure within the interested frequency range, \textit{a priori}.
Strategies such as using a sufficiently fine mesh or including a sufficient number of terms in series expansions \cite{banerjee2015dynamic} can ensure that all fully clamped frequencies are accounted for, thereby maintaining the accuracy of the algorithm. 
However, these approaches are computationally expensive and complex, posing a significant obstacle to the wider adoption and application of the DSM method based on the W-W algorithm \cite{han2018improved}.
To resolve the fully clamped plate problem, \citet{liu2015exact} suggested that the frequencies can be indirectly obtained from the simply supported plate problem, where the Navier solution serves as the analytical solution. 
This provides a significant enhancement to the W-W algorithm, increasing the efficiency of applying DSM methods. 
However, the solutions are not explicit and closed-form, but are expressed in an infinite series form, where a sufficient number of truncation terms is required to ensure accuracy.

@@

In this study, the SOV method is further extended to analyze the vibrations of plates with elastically restrained edges.
This extended SOV solution is then employed to construct the dynamic stiffness matrices, which accommodate all general homogeneous boundary conditions.
By taking advantage of both the SOV and DSM methods, an enhanced W-W algorithm is developed to solve the eigenvalue problem without directly solving the eigenvalue equations.
This enhanced approach resolves the challenge of determining fully clamped frequencies, a well-known limitation in the application of the  W-W algorithm.
In addition, a novel numerical technique is proposed to compute the mode shape coefficients.

@@

Instead of solving the free vibration of the thin orthotropic plate using \Cref{eq:governing_EOM}, it is suggested that the vibration of the thin plate can also be solved using the Rayleigh quotient variational principle \cite{xing2018overall}:
%
\begin{equation}\label{eq:Rayleigh}
	\begin{split}
		\delta U_{mag} &= \omega^2\,\delta T_0,
	\end{split}
\end{equation}
%
% It doesn't make sense to have 'mag' as a subscript - P.E. is just U, and it's already a scalar.
% And it also doesn't make sense to have '0' as the subscript for maginitude for K.E., which is just K.
% I guess you have some reason? But 'magnitude' of a scalar isn't really a thing worth highlighting.
%
where $\delta$ denotes variation, $U_{mag}$ is the magnitude of the potential energy of the plate, and $\omega^2 T_0$ represents the magnitude of the kinetic energy of the plate.
The potential energy of the plate can be expressed as \cite{xing2020extended}:
%
% What is superscript 'I' below? Why doesn't 'T' have one?
% I know you're trying to separate the two ways of calculating the same thing, but it should be consistent.
%
\begin{equation}\label{eq:poten_energy}
	\begin{split}
		U^{I} &= \frac{1}{2}\iint \Bigg[D_{11}\left(\frac{\partial^2 W}{\partial x^2}\right)^2 + 2D_{12}\frac{\partial^2 W}{\partial x^2}\frac{\partial^2 W}{\partial y^2} + D_{22}\left(\frac{\partial^2 W}{\partial y^2}\right)^2 \\
		&\qquad + 4D_{66}\left(\frac{\partial^2 W}{\partial x \partial y}\right)^2\Bigg] \, \mathrm{d}x \, \mathrm{d}y.
	\end{split}
\end{equation}
%
And the kinetic energy is:
%
\begin{equation}\label{eq:kine_energy}
	\begin{split}
		T &= \frac{1}{2}\iint \rho h \left(\frac{\partial W}{\partial t}\right)^2 \, \mathrm{d}x \, \mathrm{d}y.
	\end{split}
\end{equation}

Assuming the solution of the deflection $ W(x, y; t) = w(x, y) e^{i \omega t} $ for harmonic plate motion, 
where $ \ii = \sqrt{-1} $, $ w(x, y) $ is the mode shape, and $ \omega $ is the radial frequency.  
By substituting $ W(x, y; t) = w(x, y) e^{i \omega t} $ into \Cref{eq:poten_energy,eq:kine_energy} and expressing the system in dimensionless coordinates, we have:
%
% U sub/superscript notation hell?!
%
\begin{equation}\label{eq:poten_energy_mag}
	\begin{split}
		U_{\text{mag}}^{I} &= \frac{ab}{2} \iint \left[ \frac{D_{11}}{a^4} \left( \frac{\partial^2 w}{\partial \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2} \frac{\partial^2 w}{\partial \xi^2} \frac{\partial^2 w}{\partial \eta^2} + \frac{D_{22}}{b^4} \left( \frac{\partial^2 w}{\partial \eta^2} \right)^2 \right. \\
		&\quad \left. + \frac{4 D_{66}}{a^2 b^2} \left( \frac{\partial^2 w}{\partial \xi \partial \eta} \right)^2 \right] \, \mathrm{d} \xi \, \mathrm{d} \eta,
	\end{split}
\end{equation}
%
and
%
% Shouldn't this be U on the LHS? How can T = omega**2 T (whether T_0 or not)?
%
\begin{equation}\label{eq:kine_energy_mag}
	\begin{split}
		T &= \omega^2 \frac{ab}{2} \rho h \iint w^2 \, \mathrm{d} \xi \, \mathrm{d} \eta = \omega^2 T_0
	\end{split},
\end{equation}
%
The separable form of the mode shape function $ w(\xi, \eta)$ is given by:
%
\begin{equation}\label{eq:displace_func}
	w(\xi, \eta) = \phi(\xi) \psi(\eta),
\end{equation}
%
where $ \phi(\xi) $ and $\psi(\eta) $ can be expressed as:
\begin{subequations}\label{eq:phi_psi_solution}
	\begin{align}
		\phi(\xi) &= A_1 \sin{(\alpha_1 \xi)} + A_2 \cos{(\alpha_1 \xi)} + A_3 \sinh{(\beta_1 \xi)} + A_4 \cosh{(\beta_1 \xi)},\label{eq:phi_solution1}\\
		\psi(\eta) &= B_1 \sin{(\alpha_2 \eta)} + B_2 \cos{(\alpha_2 \eta)} + B_3 \sinh{(\beta_2 \eta)} + B_4 \cosh{(\beta_2 \eta)}. \label{eq:phi_solution2}
	\end{align}
\end{subequations}

Based on \Cref{eq:Rayleigh}, the frequencies $\omega_x$ and $\omega_y$, corresponding to the mode shapes $\phi(\xi)$ and $\psi(\eta)$, respectively, are assumed to be independent of each other.
% worth a comment here on:
% - is this a common assumption?
% - Do you later validate or check this assumption?
% - What happens if this assumption is not met?

@@

The vertical translational and rotational springs at the $\xi = -1$ end are denoted as $k^v_{\xi = -1}$ and $k^r_{\xi = -1}$, respectively, and at the $\xi = 1$ end as $k^v_{\xi = 1}$ and $k^r_{\xi = 1}$, respectively. 

@@

% What is superscript II supposed to mean?
% Why not just use U subscript x for this contribution of these supports?

@@

% Isn't this just change of variables? dimensional to non-dimensional space? Maybe say this.
% Not sure why this now deserves a 'mag' subscript.

@@

		&\qquad \left.  + \frac{4 D_{66}}{a^2 b^2} \left( \frac{\partial^2 w}{\partial \xi \partial \eta} \right)^2 \right] \, \id\xi \, \id\eta \\
		&\qquad + ab \int \left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=1}}{a} \left( w \right)^2 \right]_{\xi=1} \, \id \eta \\

@@

		U_{mag}&=\frac{ab}{2} \int_{-1}^{1} \left[ \frac{D_{11}}{a^4}I_1 \left( \frac{\id^2\phi }{\id \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2}I_2 \frac{\id^2\phi }{\id \xi^2}\phi  + \frac{D_{22}}{b^4}I_4  \phi^2 \right. \\
		&\qquad \left. + \frac{4 D_{66}}{a^2 b^2}I_3 \left( \frac{\id \phi }{\id \xi}\right)^2 \right] \, \id\xi \\
		&\qquad + abI_1 \left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=-1}}{a} \left( \phi \right)^2\right]_{\xi=-1}\\
		&\qquad + abI_1 \left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=1}}{a} \left( \phi \right)^2\right]_{\xi=1},

@@

% The notation needs to be cleaned up a bit, or more clearly defined.

@@

Taking the Rayleigh principle in the form:

@@

		\delta U_{mag} &= \omega_x^2 \, \delta T_0,

@@

and by substituting \Cref{eq:poten_energy_tolx2,eq:kine_energyx} into \Cref{eq:Rayleighx}, and relieving $\delta \phi$ and $\delta\frac{\id  \phi}{\id \xi}$ in \Cref{eq:Rayleighx} by calculus of variations, yields:

@@

% Very nice!

@@

By substituting $\phi(\xi) = A e^{\mu \xi}$ into \Cref{eq:ODEx}, we obtain:

@@

And so the solution for $\mu$ can be expressed as:

@@

		&\quad\qquad+ \frac{2k^v_{\xi=-1}}{a} I_1 \left(\phi\right)_{\xi=-1}

@@

		&\left( \frac{D_{12}}{a^2b^2} I_2 \phi + \frac{D_{11}}{a^4} I_1 \frac{\partial^2 \phi}{\partial \xi^2} \right) 
		\Big|^{\xi=1}_{\xi=-1} \\
		&\qquad + \frac{2k^r_{\xi=-1}}{a^3} I_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=-1}
		+ \frac{2k^r_{\xi=1}}{a^3} I_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=1} = 0.

@@

Substituting \Cref{eq:phi_solution1} into \Cref{eq:boundaryx}, and denoting $ k^{u*}_{\xi} \equiv \frac{2a^3 k^u_{\xi}}{D_{11}} $ for $u \in \{r,v\}$, $ S_u \equiv \sin u $, $ C_u \equiv \cos u $, $ Sh_u \equiv \sinh u$, and $ Ch_u \equiv \cosh u $, we have:

@@

However, solving these transcendental equations is cumbersome and so the DSM is introduced to avoid such a computation.

To develop the plate's dynamic stiffness matrix, with the help of \Cref{eq:phi_solution1}, the vertical displacement and rotation corresponding to the mode shape $\phi(\xi)$ along the $x$-direction at edges $\xi = -1$ and $\xi = 1$ can be expressed as:
%
% In below - isn't alpha_1/a just b?
\begin{equation}\label{eq:UBx}
	\begin{split}
		\begin{Bmatrix}
			\phi_{\xi=-1}\\\frac{\id \phi}{\id \xi}_{\xi=-1}\\\phi_{\xi=1}\\\frac{\id \phi}{\id \xi}_{\xi=1}
		\end{Bmatrix}
		= \begin{bmatrix}
			-S_{\alpha_1}&C_{\alpha_1}&-Sh_{\beta_1}&Ch_{\beta_1}\\
			\alpha_1 C_{\alpha_1}/a&\alpha_1S_{\alpha_1}/a&\beta_1Ch_{\beta_1}/a&-\beta_1Sh_{\beta_1}/a\\
			S_{\alpha_1}&C_{\alpha_1}&Sh_{\beta_1}&Ch_{\beta_1}\\
			\alpha_1 C_{\alpha_1}/a&-\alpha_1S_{\alpha_1}/a&\beta_1Ch_{\beta_1}/a&\beta_1Sh_{\beta_1}/a
		\end{bmatrix}
		\begin{Bmatrix}
			A_1\\A_2\\A_3\\A_4
		\end{Bmatrix} ,
	\end{split}
\end{equation}
%
or,
%
\begin{equation}\label{eq:UBx1}
	\mathbf{\delta}_x= \mathbf{Q}_x\mathbf{A}.
\end{equation}
%
Solving for the eigenvector $\mathbf{A}$, and then substituting into \Cref{eq:ABx1}, we obtain:
%
\begin{equation}\label{eq:DSM_eqx}
	\mathbf{R}_x \mathbf{A}=\mathbf{R}_x\mathbf{Q}_x^{-1}\mathbf{\delta}_x = \mathbf{0}.
\end{equation}
%
where the dynamic stiffness matrix, denoted as $\mathbf{K}_x = \mathbf{R}_x\mathbf{Q}_x^{-1}$, can be obtained from \Cref{eq:DSM_eqx}. 
This matrix can be used to compute the natural frequencies of the system instead of solving the eigenvalue equation, 
and the method for the computation will be given in \Cref{sec:WWA}.
